\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2021-09-15 sections/supplementary.tex
Update on Overleaf.

>>>>

  \subsection{Configuration used for MiCoNE runs}

  \subsection{Generation of sequence data}

  \subsubsection{Mock sequence data}
  Mock 4: A mock community composed of 21 bacterial strains represented in equal abundances in two replicate samples, and the same strains represented in uneven abundances in two replicate samples. These are the same community members present in mock-3 and mock-5, which consists of the same mock community samples analyzed on separate Illumina sequencing runs. This was generated by Dr. Dirk Gevers at Broad Institute in 2012. Previously called dataset-3 in [Bokulich et al. 2013](https://dx.doi.org/10.1038/nmeth.2276) and dataset B4 in [Bokulich et al. 2015](https://dx.doi.org/10.7287/peerj.preprints.934v2).

  Mock 12: Composed of 27 bacterial strains amplified with 515f/806r primers. Intended to include more closely related taxa than the other mock communities, the members of which were chosen in part for their well-separated 16S rRNA gene sequences. These strains are all distinguishable over the sequenced region of the 16S rRNA gene, but some pairs of strains differ by as little as one nucleotide. Generated by Benjamin Callahan at Stanford University in 2015. Known as "Extreme" dataset in the original publication, doi:10.1038/nmeth.3869.

  Mock 16: Mock community generated by Melanie Schirmer at University of Glasgow in 2015. Composed of even amounts of purified genomic DNA from 49 bacteria and 10 archaea. Known as dataset 35 in the original publication, doi:10.1093/nar/gku1341.

  \subsubsection{Synthetic sequence data}
  - We first create a sequence pool for various samples. This will have mutated (2\% mutation rate) reference sequences at abundances that are close to real abundances
  - We then use `art_illumina` with 1x fold_coverage to generate fastq read files for each sample.

    We created reference sequences that are 1/10th or 1/100th such that we have repeating sequences. Eg. If we have 3500 total reads, and 90\% are from same taxonomy, we have 32 or 315 reads of this sequence then we can fix `-f` as 3500/multiplier. To get multiplier we  could look at low abundant sequence and how much do we need to have atleast one of these sequences. OR should I just have fold coverage of 1x and 3500 references? Make 2\% of the positions in each sequence randomly mutate to create nucleotide diversity [source](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5967554/)

  \subsection{Generation of synthetic interaction data}
  Figures describing the original OTU tables or the interactions used to generate the community. Also include the seed and scripts for reproducing the networks.
